---
title: "MIS"
author: "John Kamau"
date: "09/08/2019"
output: word_document
---

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,fig.width = 10,fig.height = 7)
options(scipen=999)
```

```{r}
library(readxl)
library(data.table)
library(dplyr)
library(tidyr)
library(knitr,kableExtra)
library(formattable)
library(ggplot2)
library(janitor)
source('theme.R')
colors <- c("#118467", "#A9711E", "#6D847A", "#BB8755", "#82ACA0", "#9C7F61",
            "#D88523", "#83A593", "#E6A168", "#9DD0C0", "#BE9D7C", "#A2C8B9",
            "#EBCABA", "#A1DBD3")
#df <- read_excel("D:/Kamau Lift/SEEP/MIS/SEEP-MIS_DataCollection_2019_08_08_12_32.xlsx")
combined <- read_excel("D:/Kamau Lift/SEEP/combined.xlsx")
df<-combined[,grep("Country|^ID$|MIS",names(combined))]

setDT(df)

X =data.table(names(df))
X[,cleaned:=gsub("SEEP_MIS_DATACOLLECTION_","",V1)]
#view(head(X))
names(df)<-X$cleaned
```

# Q3	Is name of Group {0} ?	

```{r}
q =df[,grep("Country|Q_3$",names(df)),with =F]#[c(1,131,141:295),]
q[,Name:=ifelse(Q_3==1,"Yes",ifelse(Q_3==2,"No, please type the correct group name",ifelse(Q_3==3,"I don't know",ifelse(Q_3==4,"Does not want to answer",NA))))]
q$Name <-factor(q$Name,levels =c("Yes","No, please type the correct group name","I don't know","Does not want to answer","Respondents","Percentage"))
B = q %>%drop_na() %>%  group_by(Country,Name)  %>% dcast(Name~Country)
rbind(B,c("Respondents",colSums(B[,c(2:3)],na.rm = T))) %>% kable()
per <- B%>%  adorn_percentages('col')
per[c(1:length(per$Mali)),2:3] <-per[c(1:length(per$Mali)),2:3] %>% signif(digits=3)
rbind(per,c("Percentage",c(1,1,1,1,1,1)))  %>% kable()
```

# Q4	Is {0} your Group number?	

```{r}
q =df[,grep("Country|Q_4$",names(df)),with =F]#[c(1,131,141:295),]
q[,Name:=ifelse(Q_4==1,"Yes",ifelse(Q_4==2,"No, please type the correct group name",ifelse(Q_4==3,"I don't know",ifelse(Q_4==4,"Does not want to answer",NA))))]
q$Name <-factor(q$Name,levels =c("Yes","No, please type the correct group name","I don't know","Does not want to answer","Respondents","Percentage"))
B = q %>%drop_na() %>%  group_by(Country,Name)  %>% dcast(Name~Country)
rbind(B,c("Respondents",colSums(B[,c(2:3)],na.rm = T))) %>% kable()
per <- B%>%  adorn_percentages('col')
per[c(1:length(per$Mali)),2:3] <-per[c(1:length(per$Mali)),2:3] %>% signif(digits=3)
rbind(per,c("Percentage",c(1,1,1,1,1,1)))  %>% kable()
```

# Q5	Is your group linked to any external savings?	

```{r}
q =df[,grep("Country|Q_5",names(df)),with =F]#[c(1,131,141:295),]
G =copy(q)
names(q) =c("Country","bank-account","microfinance account","SACCO account","mobile money","other (specify)","none")
q =melt(q,id.vars ='Country')
q[,Value:=ifelse(value==0,"No","Yes")]
q$variable<-factor(q$variable,levels =c("bank-account","microfinance account","SACCO account","mobile money","other (specify)","none"))
q %>% drop_na() %>% ggplot(aes(x=variable,fill =Value))+geom_bar(position ="fill")+facet_wrap(~Country)+theme1+scale_fill_manual(values=colors)+
  labs(title="Is your group linked to any external savings?	SEEP-MIS-05",x='External Accounts:         ')
G %>% drop_na() %>% group_by(Country) %>% tally()
```

# Q6	Is your group linked to any external credit/loans?

```{r}
q =df[,grep("Country|Q_6",names(df)),with =F]#[c(1,131,141:295),]
G =copy(q)
names(q) =c("Country","Loan from bank","Loan from microfinance","Loan from SACCO","Loan from mobile money/digital loans","Loan from other (specify)","No loan for group")
q =melt(q,id.vars ='Country')
q[,Value:=ifelse(value==0,"No","Yes")]
q$variable<-factor(q$variable,levels =c("Loan from bank","Loan from microfinance","Loan from SACCO","Loan from mobile money/digital loans","Loan from other (specify)","No loan for group"))
q %>% drop_na() %>% ggplot(aes(x=variable,fill =Value))+geom_bar(position ="fill")+facet_wrap(~Country)+theme1+scale_fill_manual(values=colors)+
  labs(title="Is your group linked to any external credit/loans? \n SEEP-MIS-06",x='External Credit')+coord_flip()
G %>% drop_na() %>% group_by(Country) %>% tally()
```

<!-- # Q7	Date of first training meeting	 -->

<!-- ```{r} -->
<!-- library(stringr) -->
<!-- today ='2019-08-09' -->
<!-- q =df[,grep("Country|Q_7$",names(df)),with =F]#[c(1,131,141:295),] -->
<!-- q[,year:=substr(Q_7,1,4)] -->
<!-- q[,year:=ifelse(year==1900,NA,year)] -->

<!-- q %>% drop_na() %>% group_by(year,Country) %>% tally() %>% ggplot(aes(x=year,y=n,fill =colors[1]))+geom_bar(stat ='identity')+facet_wrap(~Country)+theme1+scale_fill_manual(values=colors)+labs(title ="Date of first training meeting SEEP-MIS-07",x="Year of first meeting  Mali n=181   uganda n=5",y="count")+scale_y_continuous(breaks=seq(0,100,5))+theme(legend.position = 'none')+theme(axis.text.x = element_blank()) -->
<!-- #q %>% drop_na() %>%group_by(Country) %>% count() -->

<!-- ``` -->

# Q8	Date savings started this cycle	

```{r}
library(stringr)
today ='2019-08-09'
q =df[,grep("Country|Q_8$",names(df)),with =F]#[c(1,131,141:295),]
q[,year:=substr(Q_8,1,4)]
q[,year:=ifelse(year==1900,NA,year)]
q[,time:=difftime(today,Q_8,units ="days")]
q %>% drop_na() %>% ggplot(aes(x="",y=time/30,fill =colors[1]))+geom_boxplot()+facet_wrap(~Country)+theme1+scale_fill_manual(values=colors)+labs(title ="Date savings started this cycle SEEP-MIS-08","(Mali n=150 Uganda n=7)",y="Months Ago")+scale_y_continuous(breaks=seq(0,250,1))+theme(legend.position = 'none')+coord_cartesian(ylim =c(0,20))
q %>% drop_na() %>% group_by(Country) %>% tally()
```

<!-- # Q9	Group trained by	 -->

<!-- ```{r} -->
<!-- q =df[,grep("Country|Q_9$",names(df)),with =F] -->
<!-- q[,Trainer:=tolower(Q_9)] -->
<!-- q[,Trainer:=gsub("abangi florence.","abangi florence",Trainer)] -->
<!-- q[,Trainer:=gsub("aminateur|animatri|animatrice|animateu|animat|anamateur|animateurr|animateurr","animateur",Trainer)] -->
<!-- q[,Trainer:=gsub("hamadou toumagno","hamadou toumagnon",Trainer)] -->
<!-- q[,Trainer:=gsub("kadia|kadia koné|kadia coulibaly coulibaly|kadia coulibalytou","kadia coulibaly",Trainer)] -->
<!-- q %>% group_by(Trainer,Country) %>% count() %>% dcast(Trainer~Country) -->


<!-- ``` -->

# Q10	which type of trainer did your group have?	

```{r}
q =df[,grep("Country|Q_10",names(df)),with =F]#[c(1,131,141:295),]

q[,Type:=ifelse(Q_10==1,"Field Officer: Project paid",ifelse(Q_10==2,"Village Agent: Group paid",ifelse(Q_10==3,"Village Agent: Unpaid",ifelse(Q_10==4,"Village Agent: Unknown if paid",ifelse(Q_10==5,"Spontaneous",ifelse(Q_10==6,"They don’t know",NA))))))]
q$Type<-factor(q$Type,levels =c("Field Officer: Project paid","Village Agent: Group paid","Village Agent: Unpaid","Village Agent: Unknown if paid","Spontaneous","They don’t know","Respondents","Percentage"))
B = q %>%drop_na() %>%  group_by(Country,Type) %>% dcast(Type~Country)
rbind(B,c("Respondents",colSums(B[,c(2:3)],na.rm = T))) %>% kable()
per <- B%>%  adorn_percentages('col')
per[c(1:length(per$Mali)),2:3] <-per[c(1:length(per$Mali)),2:3] %>% signif(digits=3)
rbind(per,c("Percentage",c(1,1,1,1,1,1)))  %>% kable()

```

# Q11	Members at start of cycle	

```{r}
q =df[,grep("Country|Q_11",names(df)),with =F]#[c(1,131,141:295),]

q %>% ggplot(aes(x="",y=Q_11))+geom_boxplot(fill=colors[1])+facet_wrap(~Country)+labs(title ="Members at start of cycle SEEP-MIS-11",y ="Members","Mali n=150  Uganda n =7")+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,50,5))
q %>% drop_na() %>% group_by(Country) %>% tally()
```

<!-- # Q12	Date of data collection	 -->

<!-- ```{r} -->
<!-- q =df[,grep("Country|Q_12",names(df)),with =F]#[c(1,131,141:295),] -->
<!-- H <- q %>% group_by(Country,Q_12) %>% tally() -->
<!-- setDT(H) -->
<!-- H[,months:=substr(Q_12,6,7)] -->
<!-- H[H$months=="11"]<-NA -->
<!-- H %>% drop_na() %>% ggplot(aes(x=Q_12,y=n))+geom_bar(stat ="identity",fill=colors[1])+facet_wrap(~Country)+labs(title="Date of data collection	 SEEP-MIS-12",y='Count',x ='date of Collection (Mali n=150 Uganda n=7)')+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks=seq(0,40,5)) -->
<!-- q %>% drop_na() %>% group_by(Country) %>% tally() -->
<!-- ``` -->

# Q13	Registered members at present	

```{r}
q =df[,grep("Country|Q_13",names(df)),with =F]

q %>% ggplot(aes(x="",y=Q_13))+geom_boxplot(fill=colors[1])+facet_wrap(~Country)+labs(title ="Registered members at present	 SEEP-MIS-13",y ="Members","Mali n =150 Uganda n=7")+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,50,5))
q %>% drop_na() %>% group_by(Country) %>% tally()
```

# Q14	Registered men at present	

```{r}
q =df[,grep("Country|Q_14",names(df)),with =F]

q %>% ggplot(aes(x="",y=Q_14))+geom_boxplot(fill=colors[1])+facet_wrap(~Country)+labs(title ="Registered men at present SEEP-MIS-14",y ="Members","Mali n=150 Uganda n=7")+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,50,2))
q %>% drop_na() %>% group_by(Country) %>% tally()
```

# Q15	Registered women at present	

```{r}
q =df[,grep("Country|Q_15",names(df)),with =F]#[c(1,131,141:295),]

q %>% ggplot(aes(x="",y=Q_15))+geom_boxplot(fill=colors[1])+facet_wrap(~Country)+labs(title ="Registered women at present SEEP-MIS-15",y ="Members","Mali n=150 Uganda n =7")+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,50,5))
q %>% drop_na() %>% group_by(Country) %>% tally()
```

# Q16	No. of members attending meeting	

```{r}
q =df[,grep("Country|Q_16",names(df)),with =F]#[c(1,131,141:295),]

q %>% ggplot(aes(x="",y=Q_16))+geom_boxplot(fill=colors[1])+facet_wrap(~Country)+labs(title ="No. of members attending meeting SEEP-MIS-16",y ="Members","Mali n =150 Uganda n=7")+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,50,5))
q %>% drop_na() %>% group_by(Country) %>% tally()
```

# Q17	Total number of share bought by member {0}

I sampled 1-30 of the 500 iteration to represent the general trend

```{r}
q =df[,grep("Country|Q_17",names(df)),with =F]#[c(1,131,141:295),]
q=q[,c(1:30)]
q.melt<-melt(q,id.vars="Country")
q.melt[,variables:=substr(variable,1,3)]
q.melt[,clean:=ifelse(value>1000,NA,ifelse(value<0,NA,value))]
UG<-q.melt[q.melt$Country=="Uganda"]
ML<-q.melt[q.melt$Country=="Mali"]
ML %>% ggplot(aes(x=variable,y=clean))+geom_boxplot(fill =colors[1])+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,50,1))+labs(title="Total number of share bought by member {0} SEEP-MIS-17 (Mali)",y="shares","Iterations 1-30  ")
UG %>% ggplot(aes(x=variable,y=clean))+geom_boxplot(fill=colors[1])+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,500,50))+labs(title="Total number of share bought by member {0} SEEP-MIS-17 (Uganda)",y="shares","Iterations 1-30 ")+coord_cartesian(ylim =c(0,500))
q %>% drop_na() %>% group_by(Country) %>% tally()

```

# Q18 Value of loan outstanding by member 
* Mali exchange rate 0.0017068220
* Uganda exchange rate 0.000270226

```{r}
ug =0.000270226
ml =0.0017068220
q =df[,grep("Country|Q_18",names(df)),with =F]#[c(1,131,141:295),]
q=q[,c(1:30)]
q.melt<-melt(q,id.vars="Country")
#q.melt[,variables:=substr(variable,1,3)]
UG<-q.melt[q.melt$Country=="Uganda"]
ML<-q.melt[q.melt$Country=="Mali"]
ML %>% ggplot(aes(x=variable,y=value*ml))+geom_boxplot(fill=colors[1])+theme1+scale_fill_manual(values=colors)+labs(title="Value of loan outstanding by member SEEP-MIS-18 (Mali)",y="share value in dollars",x ="Iterations 1-30 ")+coord_cartesian(ylim =c(0,50))+scale_y_continuous(breaks =seq(0,50,5))
UG %>% ggplot(aes(x=variable,y=value*ug))+geom_boxplot(fill=colors[1])+theme1+scale_fill_manual(values=colors)+labs(title="Value of loan outstanding by member SEEP-MIS-18 (Uganda)",y="share value in dollars",x ="Iterations 1-30 ")+scale_y_continuous(breaks =seq(0,75,5))+coord_cartesian(ylim =c(0,75))
q %>% drop_na() %>% group_by(Country) %>% tally()

```

# Q19	Dropouts this cycle	

```{r}
q =df[,grep("Country|Q_19",names(df)),with =F]
q %>% ggplot(aes(x="",y =Q_19))+geom_boxplot()+labs(title ="	Dropouts this cycle	 SEEP-MIS-19",y="dropouts","Mali n =150 Uganda n =7")+facet_wrap(~Country)+theme1+scale_fill_manual(values=colors)
q %>% drop_na() %>% group_by(Country) %>% tally()

```

# Q20	Value of savings this cycle	Does not want to answer


```{r}
q =df[,grep("Country|Q_20",names(df)),with =F]#[c(1,131,141:295),]
UG =q[q$Country =="Uganda"]
ML=q[q$Country =="Mali"]
ML %>% ggplot(aes(x="",y =Q_20*ml))+geom_boxplot(fill =colors[1])+labs(title ="		Value of savings this cycle	 SEEP-MIS-20 ",y="Value in dollars","n=150")+facet_wrap(~Country)+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,3000,100))
print("")
UG %>% ggplot(aes(x="",y =Q_20*ug))+geom_boxplot(fill =colors[1])+labs(title ="		Value of savings this cycle	 SEEP-MIS-20 ",y="Value in dollars","7")+facet_wrap(~Country)+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,30000,500))
q %>% drop_na() %>% group_by(Country) %>% tally()
```

# Q21	No. of loans outstanding	

```{r}
q =df[,grep("Country|Q_21",names(df)),with =F]#[c(1,131,141:295),]
q %>% ggplot(aes(x="",y =Q_21))+geom_boxplot(fill =colors[1])+labs(title ="	No. of loans outstanding	 SEEP-MIS-21 ",y="loans","Mali n=150 Uganda n =7")+facet_wrap(~Country)+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,100,5))
q %>% drop_na() %>% group_by(Country) %>% tally()
```

# Q22	Value of loans outstanding	

```{r}
q =df[,grep("Country|Q_22",names(df)),with =F]#[c(1,131,141:295),]
UG =q[q$Country =="Uganda"]
ML=q[q$Country =="Mali"]
ML %>% ggplot(aes(x="",y =Q_22*ml))+geom_boxplot(fill =colors[1])+labs(title ="		Value of loans outstanding SEEP-MIS-22 ",y="Value in dollars","n=150")+facet_wrap(~Country)+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,800,50))+coord_cartesian(ylim =c(0,800))
UG %>% ggplot(aes(x="",y =Q_22*ug))+geom_boxplot(fill =colors[1])+labs(title ="Value of loans outstanding SEEP-MIS-22 ",y="Value in dollars","n=7")+facet_wrap(~Country)+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,4000,500))+coord_cartesian(ylim =c(0,4000))
q %>% drop_na() %>% group_by(Country) %>% tally()
```

# Q23	Write-offs this cycle	

```{r}
q =df[,grep("Country|Q_23",names(df)),with =F]#[c(1,131,141:295),]
q %>% ggplot(aes(y=Q_23))+geom_boxplot(fill=colors[1])+facet_wrap(~Country)+theme1+scale_fill_manual(values =colors)+labs(title ="Write-offs this cycle	 SEEP-MIS-23",y ="writeoffs","Mali n =150  Uganda n =7")
q %>% drop_na() %>% group_by(Country) %>% count()
```

# 24	Loan fund: Cash in box/bank	

```{r}
q =df[,grep("Country|Q_24",names(df)),with =F][c(1,131,141:295),]
names(q)<-c("Country","Cash in box","cash in bank")
q.melt <-melt(q,id.vars ="Country")
UG =q.melt[q.melt$Country =="Uganda"]
ML=q.melt[q.melt$Country =="Mali"]
ML %>% ggplot(aes(x=variable,y =value*ml))+geom_boxplot(fill =colors[1])+labs(title ="	Loan fund: Cash in box/bank SEEP-MIS-24 ",y="Value in dollars","Mali n=150")+facet_wrap(~Country)+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,250,20))+coord_cartesian(ylim =c(0,250))
UG %>% ggplot(aes(x=variable,y =value*ug))+geom_boxplot(fill =colors[1])+labs(title ="	Loan fund: Cash in box/bank SEEP-MIS-24 ",y="Value in dollars","Uganda n=7")+facet_wrap(~Country)+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,500,50))+coord_cartesian(ylim =c(0,500))

q %>% drop_na() %>% group_by(Country) %>% tally()
```

# Q25	Cash in other funds	

```{r}
q =df[,grep("Country|Q_25",names(df)),with =F]#[c(1,131,141:295),]
#q.melt <-melt(q,id.vars ="Country")
UG =q[q$Country =="Uganda"]
ML=q[q$Country =="Mali"]
ML %>% ggplot(aes(x="",y =Q_25*ml))+geom_boxplot(fill =colors[1])+labs(title ="		Cash in other funds SEEP-MIS-25 ",y="Value in dollars","n =150")+facet_wrap(~Country)+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,40,2))+coord_cartesian(ylim =c(0,40))
UG %>% ggplot(aes(x="",y =Q_25*ug))+geom_boxplot(fill =colors[1])+labs(title ="	Cash in other funds SEEP-MIS-25 ",y="Value in dollars","n =7")+facet_wrap(~Country)+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,50,5))+coord_cartesian(ylim =c(0,50))
q %>% drop_na() %>% group_by(Country) %>% tally()

```

# Q26	Property at start of cycle

```{r}
q =df[,grep("Country|Q_26",names(df)),with =F]#[c(1,131,141:295),]
#q.melt <-melt(q,id.vars ="Country")
UG =q[q$Country =="Uganda"]
ML=q[q$Country =="Mali"]
ML %>% ggplot(aes(x="",y =Q_26*ml))+geom_boxplot(fill =colors[1])+labs(title ="		Property at start of cycle SEEP-MIS-26 ",y="Value in dollars","n =150")+facet_wrap(~Country)+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,40,2))+coord_cartesian(ylim =c(0,40))
UG %>% ggplot(aes(x="",y =Q_26*ug))+geom_boxplot(fill =colors[1])+labs(title ="	Property at start of cycle SEEP-MIS-25 ",y="Value in dollars","n =7")+facet_wrap(~Country)+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,50,5))+coord_cartesian(ylim =c(0,50))

q %>% drop_na() %>% group_by(Country) %>% tally()
```

# Q27	Property now

```{r}
q =df[,grep("Country|Q_27",names(df)),with =F]#[c(1,131,141:295),]
#q.melt <-melt(q,id.vars ="Country")
UG1=q[q$Country =="Uganda"]
ML=q[q$Country =="Mali"]
ML %>% ggplot(aes(x="",y =Q_27*ml))+geom_boxplot(fill =colors[1])+labs(title ="		Property now SEEP-MIS-27 ",y="Value in dollars","n =150")+facet_wrap(~Country)+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,40,5))+coord_cartesian(ylim =c(0,40))
UG1 %>% ggplot(aes(x="",y =Q_27*ug))+geom_boxplot(fill =colors[1])+labs(title ="	Property now SEEP-MIS-27 ",y="Value in dollars","n =7")+facet_wrap(~Country)+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,50,5))+coord_cartesian(ylim =c(0,50))

q %>% drop_na() %>% group_by(Country) %>% tally()
```

# Q28	Debts	


```{r}
q =df[,grep("Country|Q_28",names(df)),with =F]#[c(1,131,141:295),]
#q.melt <-melt(q,id.vars ="Country")
UG =q[q$Country =="Uganda"]
ML=q[q$Country =="Mali"]
ML %>% ggplot(aes(x="",y =Q_28*ml))+geom_boxplot(fill =colors[1])+labs(title ="		Debts SEEP-MIS-29 ",y="Value in dollars","n=150")+facet_wrap(~Country)+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,400,20))+coord_cartesian(ylim =c(0,400))
UG %>% ggplot(aes(x="",y =Q_28*ug))+geom_boxplot(fill =colors[1])+labs(title ="	Debts SEEP-MIS-29 ",y="Value in dollars","n =7")+facet_wrap(~Country)+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,1500,50))#+coord_cartesian(ylim =c(0,50))
q %>% drop_na() %>% group_by(Country) %>% tally()
```


# Q30	Your net Profit is {0} . Is that the same as you calculated yourself?	

```{r}
q =df[,grep("Country|Q_30",names(df)),with =F][,c(1:2)]#[c(1,131,141:295),]
q[,clean:=ifelse(Q_30==1,"Yes",ifelse(Q_30==2,"No",NA))]
q$clean<-factor(q$clean,levels =c("Yes","No","Respondents","Percentage"))
B = q %>%drop_na() %>%  group_by(Country,clean) %>% dcast(clean~Country)
rbind(B,c("Respondents",colSums(B[,c(2:3)],na.rm = T))) %>% kable()
# per <- B%>%  adorn_percentages('col')
# per[c(1:length(per$Mali)),2:3] <-per[c(1:length(per$Mali)),2:3] %>% signif(digits=3)
# rbind(per,c("Percentage",c(1,1,1,1,1,1)))  %>% kable()
```

# Q31	You net loss is {0} ?  What is the reason the group made a loss?

```{r}

q =df[,grep("Country|Q_31",names(df)),with =F]
q[,Reason_For_Loss:=ifelse(Q_31==1,"Theft",ifelse(Q_31==2,"Group business failure (eg bought assets and sold at a loss)",Q_31_S))]
#q$clean<-factor(q$clean,levels =c("Yes","No","Respondents","Percentage"))
B = q %>%drop_na() %>%  group_by(Country,Reason_For_Loss)  %>% dcast(Reason_For_Loss~Country)
rbind(B,c("Respondents",colSums(B[,c(2:3)],na.rm = T))) %>% kable()
# per <- B%>%  adorn_percentages('col')
# per[c(1:length(per$Mali)),2:3] <-per[c(1:length(per$Mali)),2:3] %>% signif(digits=3)
# rbind(per,c("Percentage",c(1,1,1,1,1,1)))  %>% kable()
```

# Q32	Please write the result of the hand calculation for the profit	

```{r}
q =df[,grep("Country|Q_32",names(df)),with =F]#[c(1,131,141:295),]
UG =q[q$Country =="Uganda"]
ML=q[q$Country =="Mali"]
ML %>% ggplot(aes(x="",y =Q_32*ml))+geom_boxplot(fill =colors[1])+labs(title ="Please write the result of the hand calculation for the profit SEEP-MIS-32 ",y="Value in dollars","n =150")+facet_wrap(~Country)+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,250,20))+coord_cartesian(ylim =c(0,250))
UG %>% ggplot(aes(x="",y =Q_32*ug))+geom_boxplot(fill =colors[1])+labs(title ="Please write the result of the hand calculation for the profit SEEP-MIS-32 ",y="Value in dollars","n=7")+facet_wrap(~Country)+theme1+scale_fill_manual(values=colors)+scale_y_continuous(breaks =seq(0,1500,100))+coord_cartesian(ylim =c(0,1200))
q %>% drop_na() %>% group_by(Country) %>% tally()
```



